Sequence divergence as the main determinant of sequence-structure relationships

### 2015-05-21 manuscript/manuscript.tex
Change name of tex

\graphicspath{{../../analysis/figures/}}

@@

\bibliographystyle{peerj} %"style
\bibliography{ej_manuscript_bib} %expected file "my refs.bib"

\section*{Figures}

1. WCN-Rate4site vs Variance of RateSite (Also for RSA) and CN-Rate4site vs Variance of RateSite \\
2. WCN-Entropy vs Mean Entropy  and CN-Entropy vs Mean Entropy \\
3. RSA-Entropy vs Mean Entropy \\
4. RSA vs Rate4Site \\
5. Should I make the stress  and delta delta G correlations plots for the viral sequences that would complete the story?

%    \begin{figure}[tbh]
%            \begin{center}
%            %\includegraphics[width=6.9in]{cordiv_similarities_r4sJC.pdf}
%            \includegraphics[width=6.9in]{cordiv_similarities_seqent.pdf}
%            \end{center}
%            \caption{A comparison of the strength of Spearman correlation of sequence evolutionary rates (r4sJC) with {\it side chain} Weighted Contact Number vs. correlations of other structural properties with evolutionary rates. Detailed description of the structural properties is given in Section \label{sec:mam}. The red lines in each plot represent equality line. It is evident from all plots that for any given protein in dataset, the correlation strength of one structural property is a good proxy measure of the correlation strength of any other structural property with sequence variability measures. For brevity, correlations of structure-rate4site are not shown here but are available online, also in supplementary material.}
%            \label{fig:seqent_structure_cors}
%    \end{figure}
%
%
%    \begin{figure}[tbh]
%        \centering
%        \includegraphics[width=3.6in]{/main_modulators_cormat_r4s_wcn.pdf} \\
%        \caption{{\bf The Spearman correlation matrix of the strongest sequence--structure correlations and the prominent determinants of the strengths of the corresponding relations}. The variables on the diagonal elements of the matrix from top to bottom represent respectively, the four strongest sequence--structure relations: r4sJC--wcnSC, r4sJC--varea, seqent--wcnSC, seqent--varea, followed by protein properties that modulate the strength of these relations: the correlation between r4sJC--seqent ({\it r.r4sJC.seqent}), variance of r4sJC ({\it var.r4sJC}), variance of sequence entropy ({\it var.seqent}), variance of back-bone hydrogen bond energies ({\it var.hbe}), and the fraction of amino acids in helical \& $\beta-$sheet secondary structures in the proteins ({\it mn.helix} \& {\it mn.betas} respectively).}
%        \label{fig:mainmods}
%    \end{figure}

%    \begin{figure*}[tbh]
  %      \centering
 %       \includegraphics[width=3.4in]{/validation_r_r4s_wcn_var_seqent.pdf}
 %       \caption{{\bf Sequence--structure correlation strength versus sequence divergence.} The plot illustrates the relationship between the strength of a representative sequence--structure correlation ({\it seqent--scnSC}) and the sequence divergence as measured by the variance of protein sequence entropy. The black circles represent $209$ proteins used in this work. For comparison and validation, the red circles represent data for $9$ viral proteins taken from {\color{red}shahmoradi2014xx}}.
%        \label{fig:validation}
%    \end{figure*}

%    \begin{figure}[tbh]
%        \centering
%        \includegraphics[width=7in]{/best_wcn/select_variables/boxplot_wcn_all_in_one.pdf} \\
%        \caption{NEEDS A CAPTION.}
%        \label{fig:best_wcn}
%    \end{figure}
%
%    \begin{figure*}[tbh]
%        \centering
%        \begin{tabular}{cc}
%        \includegraphics[width=3.4in]{/modulators_similarity_Sr4sJC_scors.pdf} & \includegraphics[width=3.4in]{/modulators_similarity_Sseqent_scors.pdf} \\
%        \end{tabular}
%        \caption{{\bf Spearman correlation matrices illustrating the similarity of the set of structure and sequence properties that contribute to the strength of sequence--structure relations}.  {\bf Left:} The correlation matrix for the relation of evolutionary rates ({\it r4sJC}) with structural quantities on the diagonal of the matrix. {\bf Right:} The correlation matrix for the relation of sequence entropy ({\it seqent}) with structural quantities on the diagonal of the matrix.}
%        \label{fig:simcormats}
%    \end{figure*}
%
%    \begin{figure*}[tbh]
%        \centering
%        %\begin{tabular}{cc}
%        \includegraphics[width=3.4in]{/validation_r_seqent_wcn_var_seqent.pdf}
%        %\end{tabular}
%        \caption{{\bf Sequence--structure correlation strength versus sequence divergence.} The plot illustrates the relationship between the strength of a representative sequence--structure correlation ({\it seqent--scnSC}) and the sequence divergence as measured by the variance of protein sequence entropy. The black circles represent $209$ proteins used in this work. For comparison and validation, the red circles represent data for $9$ viral proteins taken from {\color{red} shahmoradi2014xx}}.
%        \label{fig:validation}
%    \end{figure*}

>>>>

\graphicspath{{../figures/}}

@@

\bibliographystyle{peerj} %"style
\bibliography{manuscript_bib} %expected file "my refs.bib"

\cleardoublepage
\section*{Figures}

    \begin{figure}[H]
            \centerline{\includegraphics[width=4in]{mean_entropy_cn_cor.pdf}}     
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

    \begin{figure}[H]
            \centerline{\includegraphics[width=4in]{var_entropy_cn_cor.pdf}}
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

    \begin{figure}[H]
            \centerline{\includegraphics[width=4in]{mean_entropy_wcn_cor.pdf}}
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

    \begin{figure}[H]
            \centerline{\includegraphics[width=4in]{var_entropy_wcn_cor.pdf}}
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

    \begin{figure}[H]
            \centerline{\includegraphics[width=4in]{mean_entropy_rsa_cor.pdf}}
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

    \begin{figure}[H]
            \centerline{\includegraphics[width=4in]{var_entropy_rsa_cor.pdf}}
            \caption{NEED A CAPTION!!!.}
            \label{fig:seqent_structure_cors}
    \end{figure}

NEED THE RATE4SITE FIGURES
